### 2017-06-18 src/algorithm.tex
alg

We now show how to compute the optimal embedding.
Let $C(\gamma , w_p)$ denote the
optimal embedding of a $\sigma \gamma $-path into a $sw_p$-path.
Let $\pi:\beta  \to \N$ be any typological ordering of $\beta $. 
We claim that $O$ can be computed recursively as follow:
\begin{align*}
&C(\gamma , w_p) = 
\min_{\substack{
\alpha  : pi(\alpha ) \leq pi(\beta ), 
\\
vw_p \in A_p
}}
C(\alpha , u_p)
+
\argmin_{C : P_{w_p}(\beta , \gamma , C) \leq p_c(w_p)}
\\
&C(\sigma , w_p) = c(\sigma , w_p)
\end{align*}
Now, to compute the optimal embedding, one need to compute $C(\tau , t)$. 
We also note that in order to obey to the bandwidth constraints, 
one need to temporally remove all edges $\alpha \beta $ with bandwidth greater than
$b_c(v, w_p)$ from the virtual graph and only then compute $P_{w_p}(\beta , \gamma , C)$.
The above formulation is illustrated in Figure~\ref{fig:dp1}.

\begin{figure}[ht]
\centering
\input{fig-dp1}
\caption[]{
\label{fig:dp1}
The optimal embedding of a $\sigma \gamma $-path into a $sw_p$ path can be efficiently 
computed by breaking the problem into the problem of embedding a $\sigma \alpha $-path
into a $sv$-path (blue, dashed rectangles) 
and the problem of embedding a $\alpha \gamma $-path into $w_p$ (red, dotted
rectangles) where $b_d(\alpha , \beta ) \leq b_c(v, w_p)$.
}
\end{figure}

>>>>

We now show how to compute the optimal embedding.
Let $C(\gamma , w)$ denote the
optimal embedding of a $\sigma \gamma $-path into a $sw$-path.
Let $\pi:\beta  \to \N$ be any typological ordering of $\beta $. 
We claim that $O$ can be computed recursively as follow:
\begin{align*}
&C(\gamma , w) = 
\min_{\substack{
\alpha  : pi(\alpha ) \leq pi(\beta ), 
\\
vw \in A_p
}}
C(\alpha , u)
+
\argmin_{C : P_{w}(\beta , \gamma , C) \leq p_c(w)}
\\
&C(\sigma , w) = c(\sigma , w)
\end{align*}
Now, to compute the optimal embedding, one need to compute $C(\tau , t)$. 
We also note that in order to obey to the bandwidth constraints, 
one need to temporally remove all edges $\alpha \beta $ with bandwidth greater than
$b_c(v, w)$ from the virtual graph and only then compute $P_{w}(\beta , \gamma , C)$.
The above formulation is illustrated in Figure~\ref{fig:dp1}.

\begin{figure}[ht]
\centering
\input{fig-dp1}
\caption[]{
\label{fig:dp1}
The optimal embedding of a $\sigma \gamma $-path into a $sw$ path can be efficiently 
computed by breaking the problem into the problem of embedding a $\sigma \alpha $-path
into a $sv$-path (blue, dashed rectangles) 
and the problem of embedding a $\alpha \gamma $-path into $w$ (red, dotted
rectangles) where $b_d(\alpha , \beta ) \leq b_c(v, w)$.
}
\end{figure}
